Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/paper.tex
fix caption normals colormap
Update text in 4

    \begin{figure}
        \centering
        \begin{tabular}{|c||c|c|}
            \hline
            Normals & With cube edges & Flat (no shading) \\
            \hline
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-edge} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-edge} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat-edge} &
            \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat-edge} &
            \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
            \hline
        \end{tabular}
        \caption{Examples of normals computed on a cps, then on an
        tie as a color map. First set displays II normals, second set
        uses the visibility algorithm to compute them. The normals are colored
        according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$. The
        right images are the smooth version of the left images. ``Integral
        Invariant normals'' are computed using a radius of $r=4.5$, while
        our normal estimator are computed using a deviation of $\sigma=4$, and so
        a radius of $r=2\sigma=8$}
        \label{fig:normals-estimation}
    \end{figure}

@@

    II estimator is good along digitization of smooth or flat parts of
    the dice, but presents curious artefacts near sharp features
    induced by the hollowed out numbers: this is due to the nature of
    II normal estimates, which computes a PCA of a ball centered on
    the point of interest and may include points on the other side of
    the saliencies.

    CTriv estimator only performs averaging of trivial normal
    directions along the surface. It behaves much better than II near
    features (although it tends to smooth curvatures) since it does
    not use information from across the gap. However some oscillations
    of the curvatures are distinguishable especially along the flat
    parts, and some curvature estimates are erroneous on smoother
    parts (like the edge above 6 for $\kappa_2$ or several dice
    vertices).

    VN estimator takes the best of the two previous approaches. It
    remains precise and stable on smooth and flat regions, while
    perfectly delineating sharp features and holes, whatever the kind
    of estimated curvatures. Its only drawback is the computation
    time, which is [TO COMPLETE], compared to $2.3$s for II and $0.1s$
    for CTriv.

>>>>

    \begin{figure}
        \centering
        \begin{tabular}{|c||c|c|}
            \hline
            Normals & With cube edges & Flat (no shading) \\
            \hline
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-edge} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-edge} &
            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat-edge} &
            \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat-edge} &
            \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat} \\
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
            \hline
        \end{tabular}
        \caption{Examples of normals computed on a cps, then on a
        tie as a color map. First set displays II normals, second set
        uses the visibility algorithm to compute them. The normals are colored
        according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$. The
        right images are the smooth version of the left images. ``Integral
        Invariant normals'' are computed using a radius of $r=4.5$, while
        our normal estimator are computed using a deviation of $\sigma=4$, and so
        a radius of $r=2\sigma=8$}
        \label{fig:normals-estimation}
    \end{figure}

@@

    The II estimator is good along digitization of smooth or flat parts of
    the dice, but presents curious artefacts near sharp features
    induced by the hollowed out numbers: this is due to the nature of
    II normal estimates, which computes a PCA of a ball centered on
    the point of interest and may include points on the other side of
    the saliencies.

    The CTriv estimator only performs averaging of trivial normal
    directions along the surface. It behaves much better than II near
    features (although it tends to smooth curvatures) since it does
    not use information from across the gap. However some oscillations
    of the curvatures are distinguishable especially along the flat
    parts, and some curvature estimates are erroneous on smoother
    parts (like the edge above 6 for $\kappa_2$ or several dice
    vertices).

    The VN estimator takes the best of the two previous approaches. It
    remains precise and stable on smooth and flat regions, while
    perfectly delineating sharp features and holes, whatever the kind
    of estimated curvatures. Its drawback is the computation time,
    which is $52s$ for a maximal visibility distance $8$, compared to
    $2.3$s for II and $0.1s$ for CTriv. Note that the computation time
    falls back to $33s$ for a maximal distance of $6$ (and same
    $\sigma=4$) while the result is visually indistinguishable.
